# sort: Compare Strings\...\...\...\...\...

## Description

\...

## Usage

```r
xtfrm(x, ...)

## S3 method for class 'character'
sort(
  x,
  decreasing = FALSE,
  na.last = NA,
  locale = NULL,
  strength = 3L,
  alternate_shifted = FALSE,
  french = FALSE,
  uppercase_first = NA,
  case_level = FALSE,
  normalisation = FALSE,
  numeric = FALSE
)

## S3 method for class 'character'
xtfrm(
  x,
  locale = NULL,
  strength = 3L,
  alternate_shifted = FALSE,
  french = FALSE,
  uppercase_first = NA,
  case_level = FALSE,
  normalisation = FALSE,
  numeric = FALSE
)
```

## Arguments

|                     |                                                                                                                                                                                   |
|---------------------|-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| `x`                 | character vector whose elements are to be sorted                                                                                                                                  |
| `decreasing`        | single logical value; if `FALSE`, the ordering is nondecreasing (weakly increasing)                                                                                               |
| `na.last`           | single logical value; if `TRUE`, then missing values are placed at the end; if `FALSE`, they are put at the beginning; if `NA`, then they are removed from the output whatsoever. |
| `locale`            | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |
| `strength`          | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |
| `alternate_shifted` | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |
| `french`            | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |
| `uppercase_first`   | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |
| `case_level`        | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |
| `normalisation`     | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |
| `numeric`           | see [`stri_opts_collator`](https://stringi.gagolewski.com/rapi/stri_opts_collator.html)                                                                                           |

## Details

\.....Replacements for base [Comparison](https://stat.ethz.ch/R-manual/R-devel/library/base/help/Comparison.html) operators implemented with [`stri_rank`](https://stringi.gagolewski.com/rapi/stri_rank.html). [`stri_sort`](https://stringi.gagolewski.com/rapi/stri_sort.html)

order, rank - no - show example what to use\....

we need to overload the built-in C-level dispatcher because it only supports 1 argument and does not recognise the method overloaded for objects of class \'character\'\.....

Inconsistencies in base R and the way we have addressed them here:

-   collation in different locales is difficult and non-portable across platforms **\[fixed here -- using services provided by ICU\]**

-   overloading `` `xtfrm.character` `` has no effect in R, because S3 method dispatch is done internally with hard-coded support for character arguments. Thus, we needed to replace the generic `` `xtfrm` `` with the one that calls [`UseMethod`](https://stat.ethz.ch/R-manual/R-devel/library/base/help/UseMethod.html) **\[fixed here\]**

-   order has na.last=TRUE, sort removes NA\.....

-   `` `xtfrm` `` does not support customisation of the linear ordering relation it is based upon **\[fixed by introducing `...` argument to the generic\]**

## Value

\...

## Author(s)

[Marek Gagolewski](https://www.gagolewski.com/)

## See Also

The official online manual of <span class="pkg">stringx</span> at <https://stringx.gagolewski.com/>

Related function(s): [`strcoll`](strcoll.md)

## Examples

```{r echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
set.seed(123)
library('stringx')
```

```{r sort,error=FALSE}
# ...
# order, rank examples too also with dfs...
library("stringx")
x <- c("1", "10", "11", "99", "100", "101", "1000")
base::sort.default(x)
sort(x, numeric=TRUE)  # calls stringx::sort.character
xtfrm(x, numeric=TRUE)

```